Designing a Search for the BBC

### 2013-08-26 coursework.tex
Created Use Case diagram in Graphviz (PlantUML wasn't doing so well with it).
Made a lot of progress around the main designs. Just about to start talking about AJAX.

@@

A suitable approach for tackling real-word problems is \emph{Soft Systems Methodology} (SSM)
\cite{checkland2006learning}, which will allows us to stand back from
an ontological approach of defining what the search system \emph{is} or
\emph{comprises} and instead take an \emph{epistemological} view of search
as a system. With this view, we could consider a system that holistically
transforms members of the public's desires to find online content into
the consumption of that content -- whether those desires are \emph{precise}
(e.g. they want an exact article known by headline they saw earlier or a
particular programme they missed on television) or those desires are
\emph{fuzzy} (e.g. news about a certain topic, any comedy programme, learning
materials about the Industrial Revolution).

@@

@@

>>>>

\usepackage{graphicx}
\usepackage{rotating}
\usepackage{verbatim}

@@

Using \emph{Soft Systems Methodology} (SSM)
\cite{checkland2006learning}, we can stand back from
an ontological approach of defining what the search system \emph{is} or
\emph{comprises} and instead take an \emph{epistemological} view of search
as a system. With this view, we could consider a system that holistically
transforms members of the public's desires to find online content into
the consumption of that content -- whether those desires are \emph{precise}
(e.g. they want an exact article known by headline they saw earlier or a
particular programme they missed on television) or those desires are
\emph{fuzzy} (e.g. news about a certain topic, any comedy programme, learning
materials about the Industrial Revolution).

@@

The overall design objective will be to create an initial proposal for a
search application to drive the missing components within the holistic
system depicted in figure~\ref{rich-picture}. Some subsystems already
exist, e.g. for journalists to write news articles and publish them on the
BBC News website, but for the purposes of this design exercise, we will
assume no existing application to drive the search and discovery of
those websites.

It is likely that the design will look to integrate with
existing subsystems where possible rather than attempt to replicate
work already done. For example, journalists will prefer that a search
application can integrate with the system into which they are publishing
their articles instead of being required to publish their articles into
two systems.

@@

From the rich picture in figure~\ref{rich-picture}, we can attempt to
extract the activities that are clearly within the remit of a search
application. For example, the ability for editorial staff to manage
the content of the search indexes sounds like a feature the search
application would provide. Conversely, television actors and other
contributors to a programme are likely to interact only within a television
production subsystem with a producer or content editor being responsible
for publishing information about the final production's broadcast and
availability for streaming online.

This is not to say that we can simply cross off certain elements from
our depiction of the problem because they do not directly interact
with the subsystem being designed. The \emph{systems thinking} approach
advocated by Checkland \cite{checkland1999systems} encourages us to
consider the irreducible properties of each system at each level
of abstraction. Thus we need to consider not only a search application
subsystem that solves specific problems for its immediate users, but
also an application that contributes to the desirable, emergent
properties of the BBC service as a whole.

In the specific example of television programming, we need to maintain
systems thinking throughout the design process to ensure that we
create a search application that both meets the needs of the public
using the application to search for programmes and forms part of
a television production and delivery system that itself meets the
needs of the television-watching public. It is not always the case
that the holistic system will behave predictably from the behaviours
of its parts.

Thus a suitable design strategy is to apply systems design to
the search application in isolation -- as a \emph{hard problem} --
but then to use the wider system to inform, shape and evaluate that design.

Having extracted the activities that appear to pertain to the
search application directly (and the actors involved in those activities),
we can produce a use case UML diagram like that in figure~\ref{use-case}.

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{use_case.png}
  \end{center}
  \caption{Use case diagram for BBC Search application\label{use-case}}
\end{sidewaysfigure}

This illustrates only a subset of the expected behaviours for a full
BBC search application, but touches on some of the diversity of the
potential uses. For the purposes of our initial design, we can next look
into defining the system behaviour for some of these use cases.

\section{System Behaviour}

Figure~\ref{sequence-user} shows a sequence diagram defining a user
interacting with the search system and figure~\ref{sequence-producer}
shows how a TV producer indirectly interacts with search by providing
information that ultimately ends up in the search indexes.

\begin{comment}
@startuml sequence_producer.png

skinparam monochrome true

actor Producer
participant "Programmes Database" as prog
participant "Search Index Service" as service
participant "Search Indexes" as indexes

Producer ->> prog

activate prog
prog ->> service
deactivate prog

activate service
service ->> indexes
deactivate service

activate indexes
indexes -> indexes : reindex
deactivate indexes

@enduml
\end{comment}
\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_producer.png}
  \end{center}
  \caption{Sequence diagram showing publication of programme information to the search indexes\label{sequence-producer}}
\end{figure}

The key design decision in figure~\ref{sequence-producer} is the use of
asynchronous messages only. A non-blocking set of interactions such as
publish-subscribe \cite{hohpe2004enterprise} is a good way to decouple
systems that produce and store progamme information from the search
application systems. If the systems surrounding the programmes database
can be built a \emph{channel adapter} \cite{hohpe2004enterprise} to integrate
it to a messaging system, then the search indexes can receive changes to
information without actors such as TV producers, journalists and content
editors even being aware this is happening.

\begin{comment}
@startuml sequence_user.png

skinparam monochrome true

actor User
participant "BBC Website" as www
participant "Search Service" as search
participant "Search Indexes" as indexes
participant "Source Service" as source

User -> www : types query into search box
activate www

  www -> search
  activate search

    note over search
      The service may want to vary the
      query for a number of reasons such
      as the type of device the user has
      or the nature of the query itself.
    end note

    search -> search : decide query parameters

    search -> indexes : raw query
    activate indexes
    indexes --> search : list of matching items
    deactivate indexes

    loop for each item
      search -> source : Fetch more info about item
      activate source

      note right of search
        We can enrich the retrieved items with
        more information from the original source
        systems rather than replicate all domain
        knowledge in the search indexes.
      end note

      source --> search : Returns richer info
      deactivate source
    end

  search --> www : list of enriched results
  deactivate search

www --> User : search results page
deactivate www

@enduml
\end{comment}
\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_user.png}
  \end{center}
  \caption{Sequence diagram showing a user interacting with search\label{sequence-user}}
\end{sidewaysfigure}

Note in figure~\ref{sequence-user} that while the search indexes
will contain representations of content
from several source systems, the intention shown is that richer information
about the domain model will not be held in the search indexes. This goes
along with the principle of separation of concerns\cite{dijkstra1982role}
in that the search index component can focus on optimising its data
structures around retrieval. This kind of modularity also allows source
systems maintained by other teams to take the responsibility of the
accuracy of the information, which fits in with the wider holistic view
of the system in that the volume of information involved requires that
separate teams are responsible for the accuracy of their data.

This can be seen as similar to the \emph{Lazy Load} pattern
\cite{fowler2002patterns} in that the search indexes will only return
stub objects that are capable of retrieving the fuller information
to need. This, however, could lead to a lot of calls to different
service applications per page of results. This can be done in parallel, but
the fact still remains that the user has to wait for all this to
assemble before seeing even one result.

\section{Domain Model}
\begin{comment}
@startuml model.png

skinparam monochrome true
skinparam circledCharacterRadius 0
skinparam circledCharacterFontSize 0
skinparam classFontSize 20

class CreativeWork
class NewsItem extends CreativeWork
class Programme extends CreativeWork
class BlogPost extends CreativeWork
class LiveCoverage extends CreativeWork
class LiveEventPage extends CreativeWork

class Thing
class Person extends Thing
class Event extends Thing
class Place extends Thing
@enduml
\end{comment}
